LAGOS lake depth

### 2019-08-20 lagos_depth.Rmd
stash akima tests

```{r summary_stats, echo = FALSE}
paste0(round(sum(!is.na(lg_depth$maxdepth)) / nrow(lg_depth) * 100, 2),
       "% (n=", sum(!is.na(lg_depth$maxdepth)), ") of lakes have maxdepth values.")

@@

```{r papers}
knitr::kable(
  data.frame(stringsAsFactors=FALSE,
  lead_author = c("Hollister", "Heathcote", "Oliver", "Sobek", "Emmerton",
                    "Johansson", "Neumann"),
  year = c(2011L, 2015L, 2016L, 2011L, 2007L, 2007L, 1959L),
  location = c("NE/NY Huc", "Boreal Canada", "LAGOSNE", "Sweden",
                 "Canadian Arctic", "Sweden", "Global"),
  lake_numbers = c(133L, 433L, 7347L, 6618L, 81L, 105L, 107L)
))
```

>>>>

```{r summary_stats, echo = FALSE, eval=FALSE}
paste0(round(sum(!is.na(lg_depth$maxdepth)) / nrow(lg_depth) * 100, 2),
       "% (n=", sum(!is.na(lg_depth$maxdepth)), ") of lakes have maxdepth values.")

@@

```{r papers}
knitr::kable(
  data.frame(stringsAsFactors=FALSE,
  lead_author = c("Hollister", "Heathcote", "Oliver", "Sobek", "Emmerton",
                    "Johansson", "Neumann"),
  year = c(2011L, 2015L, 2016L, 2011L, 2007L, 2007L, 1959L),
  location = c("NE/NY Huc", "Boreal Canada", "LAGOSNE", "Sweden",
                 "Canadian Arctic", "Sweden", "Global"),
  lake_numbers = c(133L, 433L, 7347L, 6618L, 81L, 105L, 107L), 
  rmse_m = c(6, 1.8, 7.1, NA, NA, NA, NA)
))
```

```{r akima}
library(gfplot)
library(dplyr)
library(PBSdata)
library(akima)

bath        <- gfplot:::load_bath(utm_zone = 9) %>% 
  filter(depth > 0) %>%
  filter(X < 600) %>% filter(X > 330) %>%
  filter(Y < 5850) %>% filter(Y > 5630)
bath_interp <- akima::interp(
      x = bath$X,
      y = bath$Y,
      z = log(bath$depth),
      extrap = TRUE, linear = TRUE
    )

z   <- reshape2::melt(bath_interp$z)
z$x <- bath_interp$x[z$Var1]
z$y <- bath_interp$y[z$Var2]
z   <- rename(z, X = x, Y = y, akima_depth = value) %>%
      dplyr::select(-Var1, -Var2) %>%
  filter(!is.na(akima_depth)) %>%
  mutate(akima_depth = exp(akima_depth)) %>%
  dplyr::select(x = X, y = Y, akima_depth)
z   <- raster::rasterFromXYZ(z)

# rasterize bath object. See - https://gis.stackexchange.com/a/79074/32531
bath_ras <- rasterize(bath[,1:2], setValues(z, NA), 
                      bath$depth, fun = mean)

par(mfrow = c(1, 2))
plot(bath_ras)
plot(z)
```
